
---
title: "`r params$set_title`"
subtitle: "`r params$set_type`"
author: "`r params$OM@Source`"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true    
runtime: shiny
---

<style type="text/css">

body{ /* Normal  */
   font-size: 16px;
}
td {  /* Table  */
   font-size: 16px;
}
title { /* title */
 font-size: 26px;
}
h1 { /* Header 1 */
 font-size: 24px;
 color: DarkBlue;
}
h2 { /* Header 2 */
 font-size: 21px;
 color: DarkBlue;
}
h3 { /* Header 3 */
 font-size: 19px;
 color: DarkBlue;
}
code.r{ /* Code block */
  font-size: 16px;
}
pre { /* Code block */
  font-size: 16px
}
</style>



<br clear="both"/>

# About this document

This is a prototype of an automatic report that documents how an operating model was conditioned on data (for example by Stochastic Stock Reduction Analysis (DLMtool MCMC, Walters et al. 2003), Statistical Catch at Age (MSEtool TMB, Huynh 2018), state space delay difference model (MSEtool TMB, Huynh 2018).  

<br clear="both"/>


# Convergence diagnostics

```{r Converge,echo=F,warning=F,error=F,results='asis',fig.width=10, fig.height=12}

  nplot<-6

  out<-params$SRAinfo
  nits<-out$nits
  thin<-out$thin
  nsim<-out$nsim
  nyears<-out$nyears
  parstr<-out$parstr
  nages<-out$maxage
  burnin<-out$burnin
  SSB<-out$SSB
  PredF<-out$PredF
  CAA<-out$CAA
  CAL<-out$CAL
  Ind<-out$Ind
  mulen<-out$mulen
  CAA_pred<-out$CAA_pred
  RD<-out$RD
  CALswitch<-out$CALswitch
  CAAswitch<-out$CAAswitch
  sel<-out$sel
  SSB0<-out$SSB0
  maxage<-out$maxage
  
  col<-rep(c("blue","red","green","orange","grey","brown","pink","yellow","dark red","dark blue","dark green"),100)

  par(mfcol=c(5,2),mai=c(0.7,0.6,0.05,0.1))
  pind<-(1:(nits/thin))*thin
  matplot(pind,t(parstr[1:nplot,pind]),type='l',ylab="log R0",xlab="Iteration")
  abline(v=burnin,lty=2)
  matplot(pind,t(parstr[nsim+(1:nplot),pind]),type='l',ylab="log infl (sel)",xlab="Iteration")
  abline(v=burnin,lty=2)
  matplot(pind,t(parstr[(nsim*2)+(1:nplot),pind]),type='l',ylab="log slp (sel)",xlab="Iteration")
  abline(v=burnin,lty=2)
  matplot(pind,t(parstr[(nsim*30)+(1:nplot),pind]),type='l',ylab="recdev1",xlab="Iteration")
  abline(v=burnin,lty=2)
  matplot(pind,t(parstr[(nsim*40)+(1:nplot),pind]),type='l',ylab="recdev2",xlab="Iteration")
  abline(v=burnin,lty=2)
  
  burn<-burnin:nits
  plot(density(parstr[1:nsim,burn],adj=0.7),xlab="log(R0)",main="")
  plot(density(parstr[nsim+(1:nsim),burn],adj=0.7),xlab="inflection selectivity",main="")
  plot(density(parstr[(nsim*2)+(1:nsim),burn],adj=0.7),xlab="slope selectivity",main="")
  plot(density(parstr[(nsim*30)+(1:nsim),burn],adj=0.7),xlab="recdev1",main="")
  plot(density(parstr[(nsim*40)+(1:nsim),burn],adj=0.7),xlab="recdev2",main="")

```


# All posterior estimates

```{r Converge2,echo=F,warning=F,error=F,results='asis',fig.width=10, fig.height=12}

  par(mfrow=c(4+sum(CAAswitch,CALswitch),2),mai=c(0.65,0.6,0.02,0.1))
  qq<-apply(SSB,2,quantile,p=c(0.05,0.25,0.5,0.75,0.95))
  ylim<-c(0,max(qq))

  matplot(t(SSB[1:nplot,]),ylim=ylim,type="l",xlab="Year",ylab="SSB")
  xs<-dim(SSB)[2]
  plot(qq[3,],ylim=ylim,type='l',xlab="Year",ylab="SSB")
  polygon(c(1:xs,xs:1),c(qq[1,],qq[5,xs:1]),border=NA,col='light grey')
  polygon(c(1:xs,xs:1),c(qq[2,],qq[4,xs:1]),border=NA,col='dark grey')
  lines(qq[3,],lwd=1,col="white")

  D<-SSB/SSB0

  qq<-apply(D,2,quantile,p=c(0.05,0.25,0.5,0.75,0.95))
  ylim<-c(0,max(qq))

  matplot(t(D[1:nplot,]),ylim=ylim,type="l",xlab="Year",ylab="Depletion")
  plot(qq[3,],ylim=ylim,type='l',xlab="Year",ylab="Depletion")
  polygon(c(1:xs,xs:1),c(qq[1,],qq[5,xs:1]),border=NA,col='light grey')
  polygon(c(1:xs,xs:1),c(qq[2,],qq[4,xs:1]),border=NA,col='dark grey')
  lines(qq[3,],lwd=1,col="white")

  qq<-apply(PredF,2,quantile,p=c(0.05,0.25,0.5,0.75,0.95))
  ylim<-c(0,max(qq))

  matplot(t(PredF[1:nplot,]),ylim=ylim,type="l",xlab="Year",ylab="Fish. Mort.")
  plot(qq[3,],ylim=ylim,type='l',xlab="Year",ylab="Fish. Mort.")
  polygon(c(1:xs,xs:1),c(qq[1,],qq[5,xs:1]),border=NA,col='light grey')
  polygon(c(1:xs,xs:1),c(qq[2,],qq[4,xs:1]),border=NA,col='dark grey')
  lines(qq[3,],lwd=1,col="white")

  qq<-apply(sel,2,quantile,p=c(0.05,0.25,0.5,0.75,0.95))
  ylim<-c(0,max(qq))
  xs<-maxage
  matplot(t(sel[1:nplot,]),ylim=ylim,type="l",xlab="Age",ylab="Selectivity")
  plot(qq[3,],ylim=ylim,type='l',xlab="Age",ylab="Selectivity")
  polygon(c(1:xs,xs:1),c(qq[1,],qq[5,xs:1]),border=NA,col='light grey')
  polygon(c(1:xs,xs:1),c(qq[2,],qq[4,xs:1]),border=NA,col='dark grey')
  lines(qq[3,],lwd=1,col="white")

  RDx<-(-maxage+1):nyears

  qq<-apply(RD,2,quantile,p=c(0.05,0.25,0.5,0.75,0.95))
  ylim<-c(0,max(qq))
  xs<-dim(RD)[2]
  matplot(RDx,t(RD[1:nplot,]),ylim=ylim,type="l",xlab="Year",ylab="Rec. Dev.")
  plot(RDx,qq[3,],ylim=ylim,type='l',xlab="Year",ylab="Rec. Dev.")
  polygon(c(RDx,RDx[xs:1]),c(qq[1,],qq[5,xs:1]),border=NA,col='light grey')
  polygon(c(RDx,RDx[xs:1]),c(qq[2,],qq[4,xs:1]),border=NA,col='dark grey')
  lines(RDx,qq[3,],lwd=1,col="white")

  
  if(CAAswitch){
    
    plot(c(1,nyears),c(1,maxage),col='white',xlab="Year",ylab="Age")
    legend("top",legend="Observed composition data",bty='n')
    points(rep(1:nyears,nages),rep(1:nages,each=nyears),cex=CAA^0.5/max(CAA^0.5,na.rm=T)*1.5,
         pch=19,col=makeTransparent("dark grey",60))
  
    CAA_pred1<-CAA_pred
    CAA_pred1[CAA_pred1<0.002]<-NA
    plot(c(1,dim(CAA)[1]),c(1,dim(CAA)[2]),col='white',xlab="Year",ylab="Age")
    legend("top",legend="Predicted composition data (1 sim)",bty='n')
    points(rep(1:nyears,nages),rep(1:nages,each=nyears),
           cex=CAA_pred1[1,,]^0.5/max(CAA_pred1[1,,]^0.5,na.rm=T)*1.5, pch=19,
           col=makeTransparent("dark grey",60))
  }

```


<br clear="both"/>
# Version Notes

The package is subject to ongoing testing. If you find a bug or a problem please send a report to <t.carruthers@oceans.ubc.ca> so that it can be fixed!  

<br clear="both"/>
<br clear="both"/>
<br clear="both"/>

<hr />
```{r copyright, results='asis',echo=FALSE, size="tiny"}

  
  cat(params$SessionID)
  cat("\n\n")
  cat(params$copyright)
 

```
<hr />
