
---
title: "`r params$set_title`"
subtitle: "`r params$set_type`"
author: "`r params$OM@Source`"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true    
runtime: shiny
---

<style type="text/css">

body{ /* Normal  */
   font-size: 16px;
}
td {  /* Table  */
   font-size: 16px;
}
title { /* title */
 font-size: 26px;
}
h1 { /* Header 1 */
 font-size: 24px;
 color: DarkBlue;
}
h2 { /* Header 2 */
 font-size: 21px;
 color: DarkBlue;
}
h3 { /* Header 3 */
 font-size: 19px;
 color: DarkBlue;
}
code.r{ /* Code block */
  font-size: 16px;
}
pre { /* Code block */
  font-size: 16px
}
</style>



<br clear="both"/>

# About this document

This is a prototype of an automatic report that documents all dynamical features of an operating model whether it was defined by the Questionnaire in A1 or also conditioned using S-SRA in A2.  

<br clear="both"/>

```{r labs,echo=F,warning=F,error=F,results='asis',fig.width=9,fig.height=9}

plot(params$OM) # rmd = T

```

<br clear="both"/>


# Version Notes

The package is subject to ongoing testing. If you find a bug or a problem please send a report to <t.carruthers@oceans.ubc.ca> so that it can be fixed!  

<br clear="both"/>
<br clear="both"/>
<br clear="both"/>

<hr />
```{r copyright, results='asis',echo=FALSE, size="tiny"}

  
  cat(params$SessionID)
  cat("\n\n")
  cat(params$copyright)
 

```
<hr />
