---
title: "`r params$set_title`"
subtitle: "`r params$set_type`"
author: "`r params$OM@Source`"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true    
runtime: shiny   
---


<style type="text/css">

body{ /* Normal  */
   font-size: 16px;
}
td {  /* Table  */
   font-size: 16px;
}
title { /* title */
 font-size: 26px;
}
h1 { /* Header 1 */
 font-size: 24px;
 color: DarkBlue;
}
h2 { /* Header 2 */
 font-size: 21px;
 color: DarkBlue;
}
h3 { /* Header 3 */
 font-size: 19px;
 color: DarkBlue;
}
code.r{ /* Code block */
  font-size: 16px;
}
pre { /* Code block */
  font-size: 16px
}
</style>




```{r set options, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
knitr::opts_chunk$set(dpi=85)
#options(width = 650)
```

<br>


# About this document

This is a prototype of an automatic report that describes the results of a demonstration ancillary Indicator analysis. ancillary indicators are used to determine whether future data are characteristic of those seen in the posterior predictive distribution of the operating models. 

<br>

# Posterior Predictive Data cross-correlation plots

In this preliminary analysis, seven data types are monitored in the posterior predictive data. These are: CS = Catch Slope, CV = Catch Variability, CM = Catch Mean, IS = Index Slope, IM = Index Mean, MLS = Mean Length Slope, MLM = Mean Length. For this demonstration these data are calculated the first 6 years of the projection. The plot below shows the cloud of data points. One simulation is highlighted as a blue cross to show how real data could be evaluated for their consistency.  

<br>

```{r CC,echo=F,warning=F,error=F,message=F,fig.width=9, fig.height=9}
 
  dat<-params$dat
  dat_ind<-params$dat_ind
  MSEobj_app<-params$MSEobj_app
  
  styr=max(dat@Year)+1
  PPD<-MSEobj_app@Misc[[1]]

  # Standardization
  PPD@Cat<-PPD@Cat/PPD@Cat[,styr]
  PPD@Ind<-PPD@Ind/PPD@Ind[,styr]
  PPD@ML<-PPD@ML/PPD@ML[,styr]

  tsd= c("Cat","Cat","Cat","Ind","Ind","ML")
  stat=c("slp","AAV","mu","slp","mu", "slp")
  res<-max(dat_ind@Year-max(dat@Year))
  datayears<-dim(dat_ind@Cat)[2]

  indPPD<-getinds(PPD,styr=styr,res=res,tsd=tsd,stat=stat)

  # Standardization
  dat_ind@Cat<-dat_ind@Cat/dat_ind@Cat[,styr]
  dat_ind@Ind<-dat_ind@Ind/dat_ind@Ind[,styr]
  dat_ind@ML<-dat_ind@ML/dat_ind@ML[,styr]

  indData<-getinds(dat_ind,styr=styr,res=res,tsd=tsd,stat=stat)

  incrate<-1/3
  incProgress(incrate)
   

  CC(indPPD,indData,pp=1,res=res)
  incProgress(incrate)
```

<br>


# Outlier detection using Mahalanobis distance

The Mahalanobis distance plot shows the distances of all simulated points from the simulated mean (in multivariate space accounting for parameter correlation). To demonstrate the function, a single simulation (as above) is compared with the other simulated values. The critical value (V) is plotted here as the 95th percentile of the Mahalanobis distances. If the observed data fall outside this value the observations are considered to be outliers. 
<br>

```{r P1_LTY,echo=F,warning=F,error=F,message=F,fig.width=8, fig.height=8}

plot_mdist(indPPD,indData)
incProgress(incrate)
```


<br>


# Version Notes

The package is subject to ongoing testing. If you find a bug or a problem please send a report to <t.carruthers@oceans.ubc.ca> so that it can be fixed!  

<br clear="both"/>
<br clear="both"/>
<br clear="both"/>

<hr />
```{r copyright, results='asis',echo=FALSE, size="tiny"}

  
  cat(params$SessionID)
  cat("\n\n")
  cat(params$copyright)
 

```
<hr />
