---
params: 
    title: ""
    Pars: "`r list()`"
    plotPars: "`r list()`"
    tabs: "`r TRUE`"
    its: " `r numeric()`"
    nyears: " `r numeric()`"
    proyears: " `r numeric()`"
    date: "`r Sys.Date()`"
title: "`r params$title`"
date: "`r params$date`"
output:
  html_document
---



## Interpreting results of risk assessment

### Projection plots

The risk assessment use case provides a projection plot showing the 90% (light blue) and 50% (dark blue) probability intervals, the median estimate (white line) and two example simulations (dark blue lines).

```{r RA_Chunk1, echo=F,warning=F,error=F,message=F,results='asis', fig.width=10, fig.height=5}


MSEobj@MPs<-MSEobj_reb@MPs<-c("Current effort", "Current catches", "FMSY fishing", "Zero fishing")
BMSYproj(MSEobj,MSEobj_reb,maxcol=4)
FigInd<-FigInd+1
  
```

Figure `r FigInd`. Risk assessment projection plots for current effort (CurE), current catches (CurC), FMSY fishing (FMSYref) and zero fishing (NFref). 


### Risk assessment table

The results of the projection are also tabulated. 

Table `r TabInd`. The probability that biomass is greater than half BMSY in future years. 

```{r RA_Chunk2, echo=F,warning=F,error=F,message=F,results='asis'}

Risk_Assessment$Tabs[[1]](MSEobj,MSEobj_reb,options=list(res=5,YIU=30),rnd=1) 
TabInd<-TabInd+1
```



